---
title: "Analysis"
author: "Phuc Nguyen, Frances Hung, Ezinne Nwankwo"
date: "2/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(caret)
library(randomForest)
library(rebus)
library(mice)
library(glmnet)
library(miceadds)
library(lavaan)
library(nnet)
```

# Data Cleaning

### Load data

Split file by number of columns for each variable in Record_layout.txt file. Spaces are missing values.

```{r load_data, cache=TRUE}
read_cas <- function(folder, file, recordfile) {
  skip <- grep("--------", readLines(unz(folder, recordfile)))
  record_layout <- read.table(unz(folder, recordfile), 
                            fill = TRUE, skip = skip, header = FALSE)
  colnames(record_layout) <- c("variable_name", "start_col", "end_col", "type")
  record_layout <- record_layout %>% filter(!is.na(end_col))
  widths <- as.numeric(as.character(record_layout$end_col)) - as.numeric(as.character(record_layout$start_col)) + 1
  cas <- read.fwf(unz(folder, file), widths = widths, header	= FALSE,
                  col.names = record_layout$variable_name)
  return(cas)
}
# cas93 <- read_cas(folder = "Harvard_CAS_1993.zip", 
#                   file = "Harvard_CAS_1993/DS0001/06577-0001-Data.txt",
#                   recordfile = "Harvard_CAS_1993/DS0001/06577-0001-Record_layout.txt")
cas97 <- read_cas(folder = "Harvard_CAS_1997.zip", 
                  file = "Harvard_CAS_1997/DS0001/03163-0001-Data.txt",
                  recordfile = "Harvard_CAS_1997/DS0001/03163-0001-Record_layout.txt")
# cas99 <- read_cas(folder = "Harvard_CAS_1999.zip", 
#                   file = "Harvard_CAS_1999/DS0001/03818-0001-Data.txt",
#                   recordfile = "Harvard_CAS_1999/DS0001/03818-0001-Record_layout.txt")
# cas20 <- read_cas(folder = "Harvard_CAS_2001.zip", 
#                   file = "Harvard_CAS_2001/DS0001/04291-0001-Data.txt",
#                   recordfile = "Harvard_CAS_2001/DS0001/04291-0001-Record_layout.txt")
```

### Impute missing values

```{r}
summary_na<-function(df) {
  na_count <- colSums(apply(df, 2, is.na))
  data.frame(name = colnames(df), na_pct = na_count/nrow(df)) %>% arrange(desc(na_pct))
}
```


The survey asks students to skip some questions on purpose. We manually go through the survey to impute these values. We use MICE to impute the remaining missing values.

### CAS93

*The below code is for survey in 1993 only*

#### Section B

```{r}
# Section B
# If answer yes to B13, skip B14, B15; If answer no to B14, skip B15.
# We fill in all the skipped rows with 0 ???
cas93 <- cas93 %>% mutate(B14 = ifelse(B13 == 2, 0, B14),
                          B15_A = ifelse(B13 == 2 | B14 == 2, 0, B15_A),
                          B15_B = ifelse(B13 == 2 | B14 == 2, 0, B15_B),
                          B15_C = ifelse(B13 == 2 | B14 == 2, 0, B15_C),
                          B15_D = ifelse(B13 == 2 | B14 == 2, 0, B15_D),
                          B15_E = ifelse(B13 == 2 | B14 == 2, 0, B15_E))
```

#### Section E

```{r}
cas93 <- cas93 %>% 
    mutate(E4 = ifelse(E3 == 2, 0, E4)) %>% 
    mutate(E6 = ifelse(E5== 2, 0, E6)) %>% 
    mutate(E7 = ifelse(E5 == 2, 0, E7)) %>% 
    mutate(E8= ifelse(E5 == 2, 0, E8)) 
```

#### Section C

We first look at missing data in section C:
\begin{enumerate}
  \item If the student hasn't had >5 drinks in a row for the past two weeks, they skip C2 and C3
  \item C6: If the student is alcohol abstinent, then they skip C7-C21. If the student hasn't drank in the past year, they skip C7-C18. If the student hasn't drank in the past month, they skip C7-C11.
  \item C11: Students skip this question if they are 21 years or older
  \item C22: Students skip this question if they have not had alcohol within the past year.
\end{enumerate}


```{r}
#all columns to character columns
cas93_C<-cas93[,grepl("^C[0-9]",colnames(cas93))]

abs<-"C[7-9]|C1[0-9]|C2[0-1]"
year<-"C[7-9]|C1[0-8]"
month<-"C[7-9]|C1[0-1]"

cas93_filled<-cas93_C %>% 
  mutate_at(vars( starts_with("C2_") ), 
          list( ~replace_na(.,0) ))  %>%
  mutate_at(vars( starts_with("C3_") ), 
          list( ~replace_na(.,0) ))

#imputing infrequent drinking for skipped questions C7-C21
abs_imp<-cas93_filled[,grep(abs,colnames(cas93_filled))]
abs_imp[rowSums(is.na(abs_imp))== ncol(abs_imp),]<-0

year_imp<-abs_imp[,grep(year,colnames(abs_imp))]
abs_imp[rowSums(is.na(year_imp))== ncol(year_imp),grep(year,colnames(abs_imp))]<-0

month_imp<-abs_imp[,grep(month,colnames(year_imp))]
abs_imp[rowSums(is.na(month_imp)) == ncol(month_imp),grep(month,colnames(year_imp))]<-0

#imputing older students for C11; still need to cross check with age group variable
q_c11<-abs_imp %>% select(starts_with("C11_"))
abs_imp[rowSums(is.na(q_c11)) == ncol(q_c11),grep("C11_",colnames(abs_imp))]<-0

#imputing students who didn't drink in the last year for C22; might have to take this with a grain of salt
q_c22<-cas93_filled %>% select(starts_with("C22_"))
cas93_filled[rowSums(is.na(q_c22)) == ncol(q_c22),grep("C22_",colnames(cas93_filled))]<-0


#bind with rest of C columns
cas93_C<-cbind(cas93_filled[1:10],abs_imp[1:69],cas93_filled[80:93])

cas93_final<-cas93[,!grepl("^C[0-9]",colnames(cas93))] %>%
  cbind(cas93_C) %>%
  select(-COLL_ID)

```

### CAS 97

#### Section A

```{r}
# See which vars have lots of NA's
cas97 %>% 
  select(which(grepl("^A", colnames(.)))) %>%
  summary_na()

# Fill in NA's that mean 0
cas97 <- cas97 %>%
  mutate(A8_answered = cas97 %>%
                        select(which(grepl("^A8_", colnames(.)))) %>%
                        rowSums(na.rm = TRUE)) %>%
  mutate(A8_1 = ifelse(is.na(A8_1) & A8_answered > 0, 0, A8_1),
         A8_2 = ifelse(is.na(A8_2) & A8_answered > 0, 0, A8_2),
         A8_3 = ifelse(is.na(A8_3) & A8_answered > 0, 0, A8_3),
         A8_4 = ifelse(is.na(A8_4) & A8_answered > 0, 0, A8_4)) %>%
  # A6 should be dummified
  mutate(ones = 1) %>%
  tidyr::pivot_wider(names_from = A6, 
                     values_from = ones, 
                     values_fill = list(ones = 0), 
                     names_prefix = "A6_") %>%
  # Some NA in A7 means student lived off campus
  mutate(A7 = ifelse(is.na(A7) & A6_5 == 1, 0, A7)) %>%
  # Drop A4, A5 that are transfer questions, otherwise have to dummify
  select(-A4, -A5, -A8_answered, -A8)

# How many complete cases left?
cas97 %>%
  select(which(grepl("^A", colnames(.)))) %>%
  filter(complete.cases(.)) %>%
  nrow()
```


#### Section B

No skipped questions

For B10, an indicator is an option, fill in zero for than NA

```{r}
# Which columns in this section have lots of NA?
cas97 %>% 
  select(which(grepl("^B", colnames(.)))) %>%
  summary_na()

# Fill in NA that actually means 0
cas97 <- cas97 %>%
  mutate(B10_answered = cas97 %>%
                        select(which(grepl("^B10_", colnames(.)))) %>%
                        rowSums(na.rm = TRUE)) %>%
  mutate(B10_1 = ifelse(is.na(B10_1) & B10_answered > 0, 0, B10_1),
         B10_2 = ifelse(is.na(B10_2) & B10_answered > 0, 0, B10_2),
         B10_3 = ifelse(is.na(B10_3) & B10_answered > 0, 0, B10_3),
         B10_4 = ifelse(is.na(B10_4) & B10_answered > 0, 0, B10_4),
         B10_5 = ifelse(is.na(B10_5) & B10_answered > 0, 0, B10_5),
         B10_6 = ifelse(is.na(B10_6) & B10_answered > 0, 0, B10_6),
         B10_7 = ifelse(is.na(B10_7) & B10_answered > 0, 0, B10_7),
         B10_8 = ifelse(is.na(B10_8) & B10_answered > 0, 0, B10_8)) %>%
  select(-B10_answered)

# How many complete cases left?
cas97 %>%
  select(which(grepl("^B", colnames(.)))) %>%
  filter(complete.cases(.)) %>%
  nrow()
```

#### Section C

```{r}

```

#### Section D

```{r}
# Which columns in this section have lots of NA?
cas97 %>% 
  select(which(grepl("^D\\d", colnames(.)))) %>%
  summary_na()

cas97 <- cas97 %>%
  select(-D7_1, -D7_2, -D7_3, -D7_4)

# How many complete cases left?
cas97 %>%
  select(which(grepl("^D\\d", colnames(.)))) %>%
  filter(complete.cases(.)) %>%
  nrow()
```





#### Section E

Possible groups to consider: Female vs Male, Younger vs Older than 21 years old

```{r}
# Which columns in this section have lots of NA?
cas97 %>% 
  select(which(grepl("^E\\d", colnames(.)))) %>%
  summary_na()

cas97 <- cas97 %>%
  # Fill NA resulted from dummifying vars E23
  mutate(E23_answered = cas97 %>%
                        select(which(grepl("^E23_", colnames(.)))) %>%
                        rowSums(na.rm = TRUE)) %>%
  mutate(E23_1 = ifelse(is.na(E23_1) & E23_answered > 0, 0, E23_1),
         E23_2 = ifelse(is.na(E23_2) & E23_answered > 0, 0, E23_2),
         E23_3 = ifelse(is.na(E23_3) & E23_answered > 0, 0, E23_3)) %>%
  # Fill E27 with 0 for people less than 21 years old
  mutate(E27_A = ifelse(is.na(E27_A) & AGELT21 == 1, 0, E27_A)) %>%
  select(-E27_B, -E27_C) %>%
  # Combine E24, 25, 26: Did you get seriously injured within 6 hours of drinking: fill 0 in NA E25
  replace_na(list(E25 = 0)) %>%
  # E10-12 skipped if never had sex. Can combine E9 and E11, drop E10, E12
  mutate(E9n11 = ifelse(is.na(E11) & E9 == 1, 0, E11 + 1)) %>%
  select(-E9, -E10, -E12, -E11) %>%
  # E13-15 skipped if male
  replace_na(list(E13 = 0, E14 = 0, E15 = 0)) %>%
  # Drop E24, E26, E23_answered
  select(-E24, -E26, -E23_answered, -E23) %>%
  #create sexual assault due to drinking variable
  mutate(sex_assualt_ind = ifelse(D4_H > 0 | D4_I > 0 | E15 > 0, 1, 0))

```

#### Section F

Everything seems fine

```{r}
# Which columns in this section have lots of NA?
cas97 %>% 
  select(which(grepl("^F", colnames(.)))) %>%
  summary_na()

# Remove F70/30FRND
cas97 <- cas97 %>%
  select(-F70FRND, -F30FRND)
```

#### Section G

```{r}
cas97 <- cas97 %>% 
  mutate(G3_answered = cas97 %>%
                        select(which(grepl("^G3_", colnames(.)))) %>%
                        rowSums(na.rm = TRUE)) %>%
  mutate(G3_1 = ifelse(is.na(G3_1) & G3_answered > 0, 0, G3_1),
         G3_2 = ifelse(is.na(G3_2) & G3_answered > 0, 0, G3_2),
         G3_3 = ifelse(is.na(G3_3) & G3_answered > 0, 0, G3_3),
         G3_4 = ifelse(is.na(G3_4) & G3_answered > 0, 0, G3_4),
         G3_5 = ifelse(is.na(G3_5) & G3_answered > 0, 0, G3_5),
         ) %>%
  select(-G3_answered, -G3) %>%
  mutate(ones=1) %>%
  pivot_wider(names_from = G4,
              values_from = ones,
              values_fill = list(ones=0),
              names_prefix = "G4_") %>%  #indicators for religion
  mutate(G14_NA = as.numeric(G14==5),
         G14_none = as.numeric(G14==6),
         G15_NA = as.numeric(G15==5),
         G15_none = as.numeric(G15==6)) %>% #indicators for don't know/NA, parental drinking
  mutate(G16_none=as.numeric(G16==4)) #indicator for no family agreement about drinking
  
# Which columns in this section have lots of NA?
cas97 %>% 
  select(which(grepl("^G\\d", colnames(.)))) %>%
  summary_na()
```

Here we check for the number of complete cases after the preprocessing step above:

```{r}
cas97 %>%
  select(which(grepl("^[[:upper:]]\\d", colnames(.)))) %>%
  select(which(!grepl("^C\\d", colnames(.)))) %>% # Remove Section C for now
  filter(complete.cases(.)) %>%
  dim()
```

We only have about 7100 observations for 212 variables 

```{r}
mean(is.na(cas97$DRINKCAT))
```

There are few missing values for the response DRINKCAT

#### Multicolinearity

```{r}
cas97_noc <- cas97 %>%
  select(which(grepl("^[[:upper:]]\\d", colnames(.)))) %>%
  select(which(!grepl("^C\\d", colnames(.)))) %>% # Remove Section C for now
  filter(complete.cases(.)) %>%
  select(-A6_NA)
sort(apply(cas97_noc, 2 , sd))
```

Drop A6_NA in complete cases, because the standard deviation is 0.

Let's check the correlation between the variables

```{r}
plot_cormat <- function(X) {
  cormat <- round(cor(X), 2)
  melted_cormat <- reshape2::melt(cormat)
  ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile() + scale_fill_gradient2(low = "blue", mid = "white", high = "red")
}

plot_cormat(cas97_noc)
```

```{r}
cormat <- round(cor(cas97_noc), 2)
covvec <- cormat[upper.tri(cormat, diag = FALSE)]
hist(covvec, breaks = 50)
reshape2::melt(cormat) %>%
  filter(Var1 != Var2) %>%
  arrange(value)

check_cor <- function(df, desc = FALSE) {
  cormat <- round(cor(df), 2)
  if (desc) {
    reshape2::melt(cormat) %>%
    filter(Var1 != Var2) %>%
    arrange(desc(value))
  } else {
    reshape2::melt(cormat) %>%
    filter(Var1 != Var2) %>%
    arrange(value)
  }
 
} 
```


TODO:
- Remove G16_none?

#### MICE

We impute the rest of the missing values with MICE:

```{r}
#mice_data<-mice(cas93_final,m=4)
#MICEd_cas93<-complete(mice_data,1) %>%
#  .[,grepl("^[A-Z][1-9]",colnames(.))]
#write.mice.imputation(mi.res=mice_data, name="miced_cas93" )
```

```{r}
# MICEd_impute_C<-readRDS("MICEd_cas93.rds")
# #saveRDS(MICEd_impute_C,file="MICEd_cas93.rds")
# multinom_fit<-glmnet(MICEd_impute_C %>% mutate_each(as.numeric) %>% select(-C8) %>% as.matrix(), MICEd_impute_C %>% mutate_each(as.numeric) %>% select(C8) %>% as.matrix(), family="multinomial")
```



## Sensitivity Analysis


```{r}
# cas97_glm_full<-cas97 %>% select(grep("^[A-Z][1-9]|^DRINKCAT",colnames(.))) %>%
#   mutate(G15 = scale(G15),
#          G16 = scale(G16),
#          G17 = scale(G17),
#          G10 = scale(G10),
#          G14 = scale(G14),
#          G8 = scale(G8),
#          G9 = scale(G9),
#          G3_45 = I(G3_4 + G3_5 > 0)) %>%
#   mutate(DRINKCAT=case_when(DRINKCAT==0 ~ "nondrinker",
#                             DRINKCAT==1 ~ "light",
#                             DRINKCAT==2 ~ "med",
#                             DRINKCAT==3 ~ "heavy")) %>%
#   mutate(DRINKCAT=as.factor(DRINKCAT)) 
# 
# 
# cas97_glm_full$DRINKCAT <- relevel(cas97_glm_full$DRINKCAT, ref = "nondrinker")
# 
# naive_glm_full<-multinom(DRINKCAT ~ ., data=cas97_glm_full)
# summary(naive_glm_full)

```


We can fit a naive glm multinomial model:


```{r}
cas97_glm<-cas97 %>% select(grep("^G2|^G3|^G4|^G8|^G9|^G10|^G15|^G14|^G16|^G17|^G13|^A6|^A8|
                      ^D2|^D8|^D9|^D3|^D1|
                      ^F5|^F6|^F1|^F4|^F2|^F3|^DRINKCAT",colnames(.))) %>%
  mutate(G15 = scale(G15),
         G16 = scale(G16),
         G17 = scale(G17),
         G10 = scale(G10),
         G14 = scale(G14),
         G8 = scale(G8),
         G9 = scale(G9),
         G3_45 = I(G3_4 + G3_5 > 0)) %>%
  mutate(DRINKCAT=case_when(DRINKCAT==0 ~ "nondrinker",
                            DRINKCAT==1 ~ "light",
                            DRINKCAT==2 ~ "med",
                            DRINKCAT==3 ~ "heavy")) %>%
  mutate(DRINKCAT=as.factor(DRINKCAT)) 

cas97_glm$DRINKCAT <- relevel(cas97_glm$DRINKCAT, ref = "nondrinker")

naive_glm<-multinom(DRINKCAT ~ ., data=cas97_glm)
summary(naive_glm)

```


We also fit a LASSO model:

**cas97_glm should be run only after data-cleaning (don't run the DRINKCAT order things)**
```{r}
cas97_glm<-cas97 %>% select(grep("^G2|^G3|^G4|^G8|^G9|^G10|^G15|^G14|^G16|^G17|^G13|^A6|^A8| #family/HS and living sit
                      ^D2|^D8|^D9|^D3|^D1| #opinions
                      ^A7|^A9|^A10|       #communities
                      ^F5|^F6|^F1|^F4|^F2|^F3|^DRINKCAT",colnames(.))) %>%
  mutate(G15 = scale(G15),
         G16 = scale(G16),
         G17 = scale(G17),
         G10 = scale(G10),
         G14 = scale(G14),
         G8 = scale(G8),
         G9 = scale(G9),
         G3_45 = I(G3_4 + G3_5 > 0)) %>%
  mutate(DRINKCAT=case_when(DRINKCAT<=1 ~ "light",
                            DRINKCAT<=3 ~ "heavy")) %>%
  mutate(DRINKCAT=as.factor(DRINKCAT)) %>%
  drop_na()

naive_lasso<-cv.glmnet(x=cas97_glm %>%
                         select(-DRINKCAT) %>% 
                         mutate_each(as.numeric) %>% 
                         as.matrix(), 
                      y=cas97_glm %>% 
                        select(DRINKCAT) %>% 
                        mutate_each(as.factor) %>% 
                        as.matrix(),
                      family="multinomial")

coef(naive_lasso)
```


### Lavaan Model

#### Section A/Community Membership

```{r}
moda <- "
  # Regression
  DRINKCAT ~ A9 + comms
  # Latent variable definition
  comms =~ A10_A + A10_B +A10_C + A10_D +A10_E + A10_F +A10_G + A10_H
"
```

```{r}
DRINKCAT <- ordered(cas97$DRINKCAT)
drinkcat <- cas97 %>%
  select(grep("^A9|^A10", colnames(.))) %>%
  mutate(DRINKCAT = DRINKCAT) %>%
  filter(complete.cases(.))
fita <- sem(moda, drinkcat, ordered = c("DRINKCAT"))
summary(fita)
```

#### Section B

```{r}
modb <- "
  # Regression
  DRINKCAT ~ CollegePolicy + CityPolicy + CollegeEdu
  # Latent variable definition
  CollegePolicy =~ B1 + B2 + 
                   B9_A + B9_B + B9_C + B9_D + B9_E + B9_F + B9_G
  CityPolicy =~ B11 + B12 +
                B13_A + B13_B + B13_C + B13_D + B13_E
  CollegeEdu =~ B7 + B8
  # Variance
  CollegePolicy ~~ CollegeEdu          
"
```

```{r}
DRINKCAT <- ordered(cas97$DRINKCAT)
drinkcat <- cas97 %>%
  select(grep("^B8_B$|^B8_C$|^B12_A$|^B7_A$|^B7_B$|^B7_C$|^B7_D$|^B7_E$|^B7_F$|^B8_D$|^B12_B$|^B9_C$|^B9_G$|^B1$|^B6_A$|^B6_B$|^B9_A$|^B9_D$|^B9_E$|^B9_F$|^B13_A$|^B13_B$|^B9_B$|^B11$|^B6_E$|^B6_C$|^B13_E$|^B2$|^B3$|^B13_C$|^B13_D$|^B6_D$", colnames(.))) %>%
  mutate(
    B12 = B12_A + B12_B,
    B8 = B8_B + B8_C + B8_D,
    B7 = B7_A + B7_B + B7_C + B7_D + B7_E + B7_F
  ) %>%
  mutate(DRINKCAT = DRINKCAT) %>%
  filter(complete.cases(.))
fitb <- sem(modb, drinkcat, ordered = c("DRINKCAT"))
summary(fitb)
```



#### Section D/ Policy and Attitudes


```{r}
modd <- '
  # Regression
  DRINKCAT ~ D2 +  
            D8_A + D8_B +
            D9_A + D9_B +
            Policy + Approp_Drinks
  # Latent variable definition
  Policy =~ D3_A + D3_B + D3_C + D3_D +D3_E + D3_F + D3_G + D3_H + D3_I + D3_J  
  Approp_Drinks =~ D1_A + D1_B + D1_C + D1_D +D1_E
  # Variance
  Policy ~~ Approp_Drinks
'
```

```{r}
DRINKCAT <- ordered(cas97$DRINKCAT)
drinkcat <- cas97 %>%
  select(grep("^D2|^D8|^D9|^D3|^D1", colnames(.))) %>%
  mutate(DRINKCAT = DRINKCAT) %>%
  filter(complete.cases(.))
fitd <- sem(modd, drinkcat, ordered = c("DRINKCAT"))
summary(fitd)
```


#### Section G/Living Situation and Background


```{r}
modg <- "
  # Regression
  DRINKCAT ~ G3_1 + G3_2 + G3_3 + G3_45 +  # race
             G4_1 + G4_2 + G4_3 + G4_4 + G4_5 + G4_6 +
             Fam + HS
  # Latent variable definition
  Fam =~ G14 + G15 + G16 + G17
  HS =~ G8 + G9 + G10
  # Variance
  HS ~~ Fam
"
```


Right now, this gives output but we need more informative variables. Also, we need to make sure MICE is filling in values in a way which makes sense.

```{r}
DRINKCAT <- ordered(cas97$DRINKCAT)
drinkcat <- cas97 %>%
  select(grep("^G2|^G3|^G4|^G8|^G9|^G10|^G15|^G14|^G16|^G17|^G13|^A6|^A8", colnames(.))) %>%
  mutate(G15 = scale(G15),
         G16 = scale(G16),
         G17 = scale(G17),
         G10 = scale(G10),
         G14 = scale(G14),
         G8 = scale(G8),
         G9 = scale(G9),
         G3_45 = I(G3_4 + G3_5 > 0) # Combine native and others
         ) %>%
  mutate(DRINKCAT = DRINKCAT) %>%
  filter(complete.cases(.))
fitg <- sem(modg, drinkcat, ordered = c("DRINKCAT"))
summary(fitg)
```

#### Section F/ Wellbeing and social groups

```{r}

modf <- "
  # Regression
  DRINKCAT ~ personal_wellbeing + academic_wellbeing + social_groups + F2 + F3
  # Latent variable definition
  personal_wellbeing =~  F6_A + F6_B + F6_C + F6_D + F6_E + F6_F + F6_G + F6_H + F6_I
  academic_wellbeing =~ F1 + F4 
  social_groups =~ F5_A + F5_B + F5_C + F5_D + F5_E + F5_F + F5_G + F5_H
  # Factor covariance
  personal_wellbeing ~~ personal_wellbeing
  academic_wellbeing ~~ academic_wellbeing
  social_groups ~~ social_groups
  personal_wellbeing ~~ academic_wellbeing
  social_groups ~~ personal_wellbeing 
  social_groups ~~ academic_wellbeing
  
"
```
  


```{r}
DRINKCAT <- ordered(cas97$DRINKCAT)
drinkcat <- cas97 %>%
  select(grep("^F5_A|^F5_B|^F5_C|^F5_D|^F5_E|^F5_F|^F5_G|^F5_H|^F6_A|^F6_B|^F6_C|^F6_D|^F6_E|^F6_E|^F6_F|^F6_G|^F6_H|^F6_I|^F1|^F4|^F2|^F3", colnames(.))) %>%
  mutate(DRINKCAT = DRINKCAT) %>%
  filter(complete.cases(.))
fitf <- sem(modf, drinkcat, ordered = c("DRINKCAT"))
lavInspect(fitf, "cov.lv")
summary(fitf)
```


#### Combined Model

```{r}
fullmod <-'
  # Regression
  DRINKCAT ~ 1*comms +
            CollegePolicy + CityPolicy + CollegeEdu +
            Policy + Approp_Drinks + 
            Fam + HS +
            personal_wellbeing + academic_wellbeing + social_groups
  
  #sex_assault_ind ~ DRINKCAT + social_groups + comms          
  # Latent variable definition
  comms =~ A10_A + A10_B +A10_C + A10_D +A10_E + A10_F +A10_G + A10_H
  CollegePolicy =~ B1 + B2 + 
                   B9_A + B9_B + B9_C + B9_D + B9_E + B9_F + B9_G
  CityPolicy =~ B11 + B12 +
                B13_A + B13_B + B13_C + B13_D + B13_E
  CollegeEdu =~ B7 + B8
  Policy =~ D3_A + D3_B + D3_C + D3_D +D3_E + D3_F + D3_G + D3_H + D3_I + D3_J  
  Approp_Drinks =~ D1_A + D1_B + D1_C + D1_D +D1_E
  Fam =~ G14 + G15 + G16 + G17
  HS =~ G8 + G9 + G10
  personal_wellbeing =~  F6_A + F6_B + F6_C + F6_D + F6_E + F6_F + F6_G + F6_H + F6_I
  academic_wellbeing =~ F1 + F4 
  social_groups =~ F5_A + F5_B + F5_C + F5_D + F5_E + F5_F + F5_G + F5_H
  
  # Variance
  CollegePolicy ~~ CollegeEdu 
  Policy ~~ Approp_Drinks
  HS ~~ Fam
  personal_wellbeing ~~ personal_wellbeing
  academic_wellbeing ~~ academic_wellbeing
  social_groups ~~ social_groups
  personal_wellbeing ~~ academic_wellbeing
  social_groups ~~ personal_wellbeing 
  social_groups ~~ academic_wellbeing
'
```



```{r}
indep_vars_patterns <- "^B8_B$|^B8_C$|^B12_A$|^B7_A$|^B7_B$|^B7_C$|^B7_D$|^B7_E$|^B7_F$|^B8_D$|^B12_B$|^B9_C$|^B9_G$|^B1$|^B6_A$|^B6_B$|^B9_A$|^B9_D$|^B9_E$|^B9_F$|^B13_A$|^B13_B$|^B9_B$|^B11$|^B6_E$|^B6_C$|^B13_E$|^B2$|^B3$|^B13_C$|^B13_D$|^B6_D$|^F5_A|^F5_B|^F5_C|^F5_D|^F5_E|^F5_F|^F5_G|^F5_H|^F6_A|^F6_B|^F6_C|^F6_D|^F6_E|^F6_E|^F6_F|^F6_G|^F6_H|^F6_I|^F1|^F4|^F2|^F3|^G2|^G3|^G4|^G8|^G9|^G10|^G15|^G14|^G16|^G17|^G13|^A8|^D2|^D8|^D9|^D3|^D1|^A9|^A10"
DRINKCAT <- ordered(cas97$DRINKCAT)
SEXASSAULT <- ordered(cas97$sex_assualt_ind)
drinkcat <- cas97 %>%
  select(grep(indep_vars_patterns, colnames(.))) %>%
  mutate(G15 = scale(G15),
         G16 = scale(G16),
         G17 = scale(G17),
         G10 = scale(G10),
         G14 = scale(G14),
         G8 = scale(G8),
         G9 = scale(G9),
         G3_45 = I(G3_4 + G3_5 > 0) # Combine native and others
         ) %>%
  mutate(
    B12 = B12_A + B12_B,
    B8 = B8_B + B8_C + B8_D,
    B7 = B7_A + B7_B + B7_C + B7_D + B7_E + B7_F
  ) %>%
  scale() %>%
  as.data.frame() %>%
  mutate(DRINKCAT = DRINKCAT,
         SEXASSAULT = SEXASSAULT) %>%
  filter(complete.cases(.))
fit_full <- sem(fullmod, drinkcat, ordered = c("DRINKCAT"))
summary(fit_full)
```

```{r}
lavInspect(fit_full, "cov.lv")
```

```{r}
fitMeasures(fit_full)
```



